lab_notebook

### 2018-11-14 lab_notebook.Rmd
in progress

@@

>>>>

edf_turf_simple <- edf_turf_unite %>%
  add_column("turf") %>%
  select("country", "start_date", "SciName") %>%
  gsub('\\bNA NA\\b', 'NA')

@@

################
################
###############
PART 2

From updating_projection.R script file
```{r}

#Load Data
#Upside data
projection_data <- readRDS("data/projection_data.rds")

#RAM Data Tiddying
ram <- timeseries_values_views %>%
  select("stocklong", "year", "TBbest", "TCbest", "BdivBmsypref", "UdivUmsypref") %>%
  add_column("RAM")

#Update Projection with RAM
projection_updated <- join(projection_data, ram, by = c("CommName", "Year"), type = "full")

#Merge Projection and ITQ
#seperate out IdOrig column for Projection Data
separate_projection <- projection_updated %>% separate(IdOrig, c("agency", "stock", "t0", "tf", "data_enterer"))

#Simplified Projection Data
ITQ_projection_simple <- ITQ_projection %>%
  select("Country", "Year", "CommName", "SciName", "SpeciesCat", "CatchShare", "Catch", "Biomass", "BvBmsy", "FvFmsy","MSY", "Price", "g", "k", "c", "phi", "yearitq", "itq_now","iq", "itq", "ivq", "turf", "programstart")

#create RDS from datafram
#saveRDS(ITQ_projection_simple, "projection_updated.rds")

1) pull the ITQ, IVQ, IQ fisheries out of upside.
2) pull the TURF fisheries from EDF.
3) For each fishery, we want species, location, and ITQ vs. TURF.

```{r}

# create dataframe with 
itq <- ITQ_projection %>%
  select("Country", "Year", "CommName", "SciName", "SpeciesCat", "CatchShare", "yearitq", "itq_now","iq", "itq", "ivq", "turf", "programstart")

#Load EDF TURF data

edf_turf <- read_excel("data/EDF_TURF_data.xlsx")

```{r}

colnames(edf_turf_simple) <- c("Country", "programstart", "SciName")

edf_projection_1 <- join(edf_turf_simple, itq, by = c("Country", "programstart", "SciName"), type = "full")
